Improving Usability of Remote Access to Sensitive Data

### 2014-07-29 ccsw14/paper.tex
added deployment example figure

The major element that is used to isolate VMs that are in the middle of
accessing sensitive data is live migration \cite{migration-clark}.  When a VM
switches from maintenance mode to secure mode, the underlying virtual machine
manager migrates that VM to a separate physical machine that has access to the
sensitive data, but which is configured to lack network access for any purpose
other than to receive other incoming VM migrations.  In other words, VMs in
maintenance mode are strictly segregated within separate physical machines from
VMs running in secure mode.  We can therefore refer to a physical machine
running only maintenance VMs as a \emph{maintenance machine}, and likewise a
\emph{secure machine} runs only secure mode instantiations of VMs.

>>>>

The major element that is used to isolate VMs that are in the middle of
accessing sensitive data is live migration \cite{migration-clark}.  When a VM
switches from maintenance mode to secure mode, the underlying virtual machine
manager migrates that VM to a separate physical machine that has access to the
sensitive data, but which is configured to lack network access for any purpose
other than to receive other incoming VM migrations.  In other words, VMs in
maintenance mode are strictly segregated within separate physical machines from
VMs running in secure mode.  We can therefore refer to a physical machine
running only maintenance VMs as a \emph{maintenance machine}, and likewise a
\emph{secure machine} runs only secure mode instantiations of VMs.  We illustrate an example deployment in Figure \ref{fig:configuration}.

\begin{figure}[ht!]
\center
\includegraphics[width=3.0in]{figures/configuration}

\caption{An example deployment configuration for a Data Capsules system.
Dotted boxes denote physical separation, which is necessary between maintenance
machines, secure machines, and the remote access proxy.  The sensitive data
server may exist separately, or it may reside on one of the secure machines.
The only connections between maintenance and secure machines will be for the
purpose of tranferring virtual machine state to secure machines, and for
read-only accesses to the VM disk images.  This data largely travels in one
direction, from maintenance machines to secure machines.}

\label{fig:configuration}
\end{figure}
